sWGS validation report

### 2019-08-30 Paper.Rmd
trying fourier transform smoothing

# for (i in 1:nrow(sum.patient.data)) {
#   print(i)
#   pt = sum.patient.data[i, 'Patient']
#   status = sum.patient.data[i, 'Status']
# 
#   pms = mtn.spatial(subset(globalCNdf, Patient == pt & seg.type != 'arms'), back, ogjLimits, paste('Patient', pt, '(', status, ')' ))
#   
#   fl = paste('patient_', pt, '.png', sep='')
#   ggsave(paste('plots/spatial/', fl, sep=''), plot=grid.arrange(pms$grob), width=14, height=6, units='in', dpi=300)
# }

@@

predicted = '~/Data/BarrettsProgressionRisk/Analysis/training/val_predictions'

>>>>

for (i in 1:nrow(sum.patient.data)) {
  print(i)
  pt = sum.patient.data[i, 'Patient']
  status = sum.patient.data[i, 'Status']

  pms = mtn.spatial(subset(globalCNdf, Patient == pt & seg.type != 'arms'), back, ogjLimits, paste('Patient', pt, '(', status, ')' ))

  fl = paste('patient_', pt, '.png', sep='')
  ggsave(paste('plots/spatial/', fl, sep=''), plot=grid.arrange(pms$grob), width=14, height=6, units='in', dpi=300)
}

@@

predicted = '~/Data/BarrettsProgressionRisk/Analysis/training/val_predictions/0.9'

### 2019-08-30 Validation Report.Rmd
trying fourier transform smoothing

source('lib/common_plots.R')

@@

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation'

@@

batch8_preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(on$`Patient ID`), collapse='|'), list.files(preds.dir, full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f, col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2)

@@

oldp.preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(oldp$`Patient ID`), collapse='|'), list.files(preds.dir, full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f,col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2) %>% dplyr::select(-Endoscopy)

@@

new.np.preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(new.np$`Patient ID`), collapse='|'), list.files(preds.dir, full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f,col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2) %>% dplyr::select(-Endoscopy)

@@

@@

>>>>

source('lib/common_plots.R')
source('lib/load_patient_metadata.R')

@@

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf'

@@

batch8_preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(on$`Patient ID`), collapse='|'), list.files(preds.dir, 'predictions.tsv', full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f, col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2)

@@

oldp.preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(oldp$`Patient ID`), collapse='|'), list.files(preds.dir, 'predictions.tsv', full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f,col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2) %>% dplyr::select(-Endoscopy)

@@

new.np.preds = do.call(bind_rows,
  purrr::map(grep( paste(unique(new.np$`Patient ID`), collapse='|'), list.files(preds.dir, 'predictions.tsv', full.names = T, recursive = T), value=T), function(f) {
             read_tsv(f,col_types = cols(
                Sample = col_character(),
                Probability = col_double(),
                `Relative Risk` = col_double(),
                Risk = col_character(),
                `Hospital Research ID` = col_character(),
                `Block ID` = col_character(),
                Endoscopy = col_date(format = ""),
                Pathology = col_character(),
                `SLX-ID` = col_character(),
                `Index Sequence` = col_character(),
                `Path Notes` = col_character()
      ))
})) %>% dplyr::mutate_if(is.numeric, list(round), 2) %>% dplyr::select(-Endoscopy)

@@

fpr.patients = new.np.preds %>% 
  group_by(`Hospital Research ID`) %>% dplyr::summarise(
  FPR = length(which(Risk == 'High'))/n() ) %>% 
  dplyr::summarise( 'Misclassified patients' = length(which(FPR > 0.5))/n() ) %>% pull %>% round(2)

@@

## Compared to the 'test' cohort

These are the patients that Ellie and I randomly assigned as a test set.  They are not part of the model training (in this version) and so are a good comparison for the validation data. These are what we might have expected to see.

predicted = '~/Data/BarrettsProgressionRisk/Analysis/training/val_predictions/0.9'

info.dir = '~/Data/BarrettsProgressionRisk/QDNAseq'

patient.file = list.files(info.dir, pattern='All_patient_info.xlsx', recursive=T, full.names=T)
demo.file = list.files(info.dir, pattern='Demographics_full.xlsx', recursive=T, full.names=T)

validation.patient.info = read.patient.info(patient.file, demo.file, set='Test')$info %>% 
  dplyr::select(Hospital.Research.ID, Patient, Path.ID, Status, Endoscopy.Year, Pathology, Plate.Index, SLX.ID, Samplename)

vpd = do.call(bind_rows, lapply(list.files(predicted, full.names = T), function(f) {
  read_tsv(f, col_types = 'cddcccdccdc')
})) %>% dplyr::select(Hospital.Research.ID, everything())

vpd = left_join(vpd %>% dplyr::select(-Pathology, -matches('P53')), 
                validation.patient.info %>% 
                  dplyr::select(Hospital.Research.ID, Patient, Status) %>% unique, by=c('Hospital.Research.ID'))

vpd %>% dplyr::group_by(Status, Risk) %>% dplyr::summarise(n=length(Risk)) %>% spread(Risk, n) %>% kableExtra::kable(caption = "Test set samples (Ellie's)") %>% kableExtra::kable_styling(full_width = F)

roc = pROC::roc(Status ~ Probability, data = vpd, auc=T, ci=T, of='thresholds',transpose=T)
roc.plot(roc)
